Approximation as Differentiation

### 2025-04-01 notes/sec/cmon-enriched.tex
Notation for V-enriched functor category.

If $C$ is $\CMon$-enriched then there is an enriched version of its Yoneda embedding, namely the
$\CMon$-enriched functor $\Yoneda_{\CMon}: \Func{C^\op}{\CMon}$

>>>>

If $C$ is $\CMon$-enriched then there is an enriched version of its Yoneda embedding, namely the
$\CMon$-enriched functor $\Yoneda_{\CMon}: \Func{C^\op}{\CMon}_{\CMon}$
